---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# RoMEO 
Retracing of Mapping Explicit to Objects (RoMEO)

## Overview
Extract relevant information from SQL scripts such as source and target tables. 

## Assumptions
- **Target table name:** In each sql script the target table name can be derived from the create (table, view, procedure) statement.

## Configuration of patterns
**Unvalid patterns:**
```{r, echo = FALSE, results='asis'}
library(knitr)
pat <- "^.*Users.*?([A-Z]+).*"
username <- gsub(pat, "\\1", getwd())
filepath_root <- paste0("C:/Users/",username,"/Desktop/")
unvalid_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_unvalid_pattern.csv"), head = FALSE)
knitr::kable(unvalid_pattern)
```
**Valid patterns:**
```{r, echo = FALSE, results='asis'}
valid_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_valid_pattern.csv"), header = FALSE)
knitr::kable(valid_pattern)
```
**Filter patterns:**
```{r, echo = FALSE, results='asis'}
filter_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_filter_pattern.csv"), header = FALSE)
knitr::kable(filter_pattern)
```
**Aggregation patterns:**
```{r, echo = FALSE, results='asis'}
aggregation_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_aggregation_pattern.csv"), header = FALSE)
knitr::kable(aggregation_pattern)
```
**Create patterns:**
```{r, echo = FALSE, results='asis'}
create_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_create_pattern.csv"), header = FALSE)
knitr::kable(create_pattern)
```
**Insert patterns:**
```{r, echo = FALSE, results='asis'}
insert_pattern <- read.csv(paste0(filepath_root,"ROMEO/romeo_insert_pattern.csv"), header = FALSE)
knitr::kable(insert_pattern)
```

## Open issues
1. **Multiple *insert into* statements**: SQL scripts can have multiple insert statements. This implies that the relation is $n x m$ for $n$ = target table and $m$ = source table.
2. **Scripts without *from* statements**: SQL scripts can just serve the sole purpose to calculate are prepare something and do not refer to a source table load.
3. **Selected attributes**: Selected attributes shall be extracted and thus create per script with one target table and one source table a $1 x n x m$ relation with 1 = target table, $n$ = source table(s), and $m$ = attribute(s).
4. **Automated join loop**: Extracted SQL script shall be joined until end.
5. **Re-organization of columns in output**: Columns in the output table shall reflect lineage steps or layer design (however in legacy systems layer design is often violated).